The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-12 albatros_paper.tex
HCC added a few more placeholder words in section 1

Very few experiments have measured the radio sky at $\lesssim 30$~MHz;
here, we highlight only four specific examples.  At the very lowest
frequencies, the state of the art among ground-based measurements
dates from the 1950s, when Reber and Ellis caught brief glimpses of
the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
space-based missions have also performed measurements at similarly low
frequency ranges; for example, the Radio Astronomy Explorer-2 operated
at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist mainly at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.  As a first step
toward laying the groundwork for possible future cosmological
measurements,...finish this sentence...

\attention{More text about the science case, including
  Galactic astrophysics (Jon? Jeff?)}

>>>>

Very few experiments have measured the radio sky at $\lesssim 30$~MHz;
here, we highlight only four specific examples.  At the very lowest
frequencies, the state of the art among ground-based measurements
dates from the 1950s, when Reber and Ellis caught brief glimpses of
the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
space-based missions have also performed measurements at similarly low
frequency ranges; for example, the Radio Astronomy Explorer-2 operated
at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
resolution finer than few-degree scales exist mainly at higher
frequencies.  For example, the Dominion Radio Astrophysical
Observatory surveyed the northern sky at \SI{22}{\MHz} with
\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
and most recently, the Owens Valley Long Wavelength Array mapped the
sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
list is not comprehensive, it does illustrate the dearth of
information about the $\lesssim 30$~MHz sky and the lack of high
resolution measurements at the lowest frequencies.  The first step
toward laying the groundwork for possible future cosmological
measurements is obtaining an improved map of Galactic foregrounds at
$\lesssim 30$~MHz.  Maps at these frequencies can additionally shed
new light on Galactic astrophysics, including cosmic ray structure
along the line of sight (\attention{more words here about synchrotron
  self-absorption}), \attention{words here about radio recombination
  lines}.  \attention{More words here about possible ionospheric
  studies.}
